Exposure Consequences - Statistics and Figures

### 2018-05-10 ManuscriptMaterials.Rmd
Added option for plot functions to create SVG files instead of creatng output in notebook / R.

```{r fig2_reachaftereffect, fig.width=7.5, fig.height=4}
plotReachAftereffects()
```

@@

```{r scattergrams, fig.width=7.5, fig.height=4}
correlations <- correlateNoCursorsLocalization()
```

@@

>>>>

```{r fig2_reachaftereffect, fig.width=7.5, fig.height=2.5}
plotReachAftereffects()
```

@@

```{r scattergrams, fig.width=7.5, fig.height=2.5}
correlations <- correlateNoCursorsLocalization()
```

@@

# Figures

Here we simply generate the same figures as above, but now they are saved as SVG files.

```{r create_svgs}
plotReachAftereffects(generateSVG=TRUE)
plotLocalization(classicOnline=TRUE, generateSVG=TRUE)
correlations <- correlateNoCursorsLocalization(generateSVG=TRUE)
```
